---
title: "Green Jobs and Growth"
subtitle: "Making the West of England the home for green jobs and growth"
author: "SC"
date: last-modified
execute:
  echo: false
  warning: false
  message: false
---

## Context

This chapter tracks indicators related to green economy and environmental sustainability across the West of England. Topics include carbon emissions, renewable energy, water pollution, climate resilience and public health.

```{r}
#| label: setup
#| code-summary: "Load required packages and source files"
#| include: false

# Load required packages
library(tidyverse)

# Source shared helpers (theme, helpers, fact_helpers, collate_fact)
source(here::here("scripts", "R", "_common.R"))
# source(here::here("scripts", "R", "load_pins.R"))
source(here::here("scripts", "R", "05-environment", "RI_5_ghg_emissions.R"))
source(here::here("scripts", "R", "05-environment", "RI_5A1_renewable.R"))
source(here::here("scripts", "R", "05-environment", "RI_5B1_nondom_epc_a.R"))
source(here::here("scripts", "R", "05-environment", "RI_5E1_heat_stress_deaths.R"))
source(here::here("scripts", "R", "05-environment", "RI_5E2_flood_warning_index.R"))
source(here::here("scripts", "R", "05-environment", "RI_5F1_tree_canopy.R"))
source(here::here("scripts", "R", "05-environment", "RI_5F4_water_catchment_health.R"))

indicator_fact_tbl <- collate_fact() |>
  build_reporting_view()
```

---

## Greenhouse Gas Emissions

```{r}
#| label: RI_5_ghg_emissions_gt
#| eval: true
#| code-summary: "RI_5_ghg_emissions KPI summary"
indicator_fact_tbl |>
format_indicator_summary(
  "RI_5_ghg_emissions",
  title = "Greenhouse Gas Emissions",
  subtitle = "Transport, Commercial, Industry, Public sector, Domestic",
  units = "Kt CO2e"
)
```

### Overview

Regional greenhouse gas emissions from transport, domestic, commercial, industrial and public sectors. This tracks the region's progress toward the net zero target by 2030 and identifies key sectors for emissions reduction.

```{r}
#| label: RI_5_ghg_emissions
#| eval: true
#| code-summary: "RI_5_ghg_emissions analysis"
#| fig-alt: |
#|   Stacked bar chart of greenhouse gas emissions by sector in the West of
#|   England Combined Authority area, 2014 to 2023. The y-axis shows emissions
#|   in kilotonnes of CO2 equivalent; the x-axis shows year. Five sectors are
#|   colour-coded: Transport (green, largest), Domestic (red), Commercial
#|   (dark green), Industry (purple), and Public Sector (black). Total
#|   emissions declined from around 6,000 kt CO2e in 2014 to approximately
#|   4,400 kt CO2e in 2023, though the region is not on track to meet its 2030
#|   net zero target. Transport and domestic heating remain the dominant
#|   sectors.
RI_5_plot
```

### Findings

Emissions have declined steadily over several years. Transport and domestic sectors dominate. The region is currently not on track to meet the 2030 net zero target, indicating a need for accelerated action in key sectors.
Demand reduction for personal car use and the introduction of low - carbon heating for homes remain key priorities for the region.

---

## Renewable Energy

```{r}
#| label: RI_5A1_renewable_gt
#| eval: true
#| code-summary: "RI_5A1_renewable summary"

indicator_fact_tbl |>
format_indicator_summary(
  "RI_5A1_renewable_capacity_km2",
  title = "Renewable Electricity Installed Capacity",
  subtitle = "Installed capacity per square Km",
  units = "MW/km2"
)

```
### Overview

Potential for renewable energy capacity is strongly influenced by land availability and price, hence this indicator is expressed in terms of Megawatts per square Kilometre to enable future comparison with other regions.

```{r}
#| label: RI_5A1_renewable_plot
#| eval: true
#| code-summary: "RI_5A1_renewable plot bar chart"
#| fig-alt: |
#|   Stacked bar chart of renewable electricity installed capacity in
#|   Megawatts by local authority in the West of England, from 2015 to 2024.
#|   The y-axis shows capacity in MW; the x-axis shows year. South
#|   Gloucestershire (dark green) contributes the largest share, followed by
#|   North Somerset (black), Bristol (red), and Bath and North East Somerset
#|   (purple). Total installed capacity grew steadily from around 250 MW in
#|   2015 to over 525 MW in 2024, reflecting the region's ambitions for net
#|   zero.

RI_5A1_renewable_plot
```

### Findings

Installed capacity has climbed steadily over the last 10 years, reflecting central government policy and the region's ambitions for Net Zero. The National Energy Systems Operator (NESO) is currently developing [regional energy strategic plans](https://www.neso.energy/what-we-do/strategic-planning/regional-energy-strategic-planning-resp) which may drive further growth in installed capacity.

---

## Domestic Renewable Energy

```{r}
#| label: RI_5A2_domestic_renewable_gt
#| eval: true
#| code-summary: "RI_5A2_domestic_renewable summary"

indicator_fact_tbl |>
format_indicator_summary(
  "RI_5A2_domestic_renewable",
  title = "Domestic Renewable Energy",
  subtitle = "Photovoltaic sites",
  units = "Sites per household"
)

```
### Overview

Solar photovoltaic (PV) installations are a key aspect of energy security and net zero. This indicator tracks installations per household in the region.

```{r}
#| label: RI_5A2_domestic_renewable_plot
#| eval: true
#| code-summary: "RI_5A2_domestic_renewable plot bar chart"
#| fig-alt: |
#|   Stacked bar chart of photovoltaic (PV) site counts by local authority in
#|   the West of England, from 2015 to 2024. The y-axis shows the number of
#|   sites; the x-axis shows year. North Somerset (black) has the largest
#|   share, followed by Bristol (red), Bath and North East Somerset (purple),
#|   and South Gloucestershire (dark green). Total PV sites increased steadily
#|   from around 16,000 in 2015 to over 36,000 in 2024, indicating consistent
#|   growth in domestic solar adoption.
RI_5A2_domestic_renewable_plot

```

### Findings

Installations of PV panels have increased steadily over the last 10 years.

---

## Non-Domestic Energy Performance

```{r}
#| label: RI_5B1_nondom_epc_a_gt
#| eval: true
#| code-summary: "summary"

indicator_fact_tbl |>
format_indicator_summary(
  "RI_5B1_nondom_epc_a",
  title = "Non - Domestic Energy Ratings",
  subtitle = "Proportion of properties rated A or A+",
  units = "%"
)

```

### Overview

This indicator measures the energy efficiency of non - domestic property by expressing the proportion of properties which have an energy rating of A or A+, in other words the best performing properties.

```{r}
#| label: RI_5B1_nondom_epc_a_plot
#| eval: true
#| code-summary: "RI_5B1_nondom_epc_a monthly cumulative plot"
#| fig-alt: |
#|   Line chart showing the cumulative monthly proportion of non-domestic
#|   properties in the West of England with an EPC energy rating of A or A+,
#|   from 2017 to 2026. The y-axis shows percentage from 0% to 100%; the
#|   x-axis shows date. The line rises very gradually from under 2% to
#|   approximately 6% by 2026, showing slow but steady improvement in the
#|   proportion of best-performing non-domestic buildings.
RI_5B1_nondom_epc_a_plot

```

### Findings

The improvement in the proportion of properties meeting an A or A+ standard is slow but steady. WECA's Low Carbon Business Support team help businesses improve their energy efficiency with assessments, advice and grants.

---


## Heat Associated Mortality

```{r}
#| label: RI_5E1_heat_stress_deaths_gt
#| eval: true
#| code-summary: "summary"

indicator_fact_tbl |>
format_indicator_summary(
  "RI_5E1_heat_stress_deaths",
  title = "Heat Associated Mortality",
  subtitle = "Deaths per million population",
  units = "deaths per million"
)

```

### Overview
This indicator tracks the number of heat associated deaths per million population in the Avon Local Resilience Forum area, which largely correlates with the West of England. It provides insight into the region's vulnerability to heat stress through the lens of public health. Data for the region are only available since 2024.

```{r}
#| label: RI_5E1_heat_stress_deaths_plot
#| eval: true
#| code-summary: "RI_5E1_heat_stress_deaths plot"
#| fig-alt: |
#|   Line and point chart showing heat-associated mortality in the Avon Local
#|   Resilience Forum area for 2024 and 2025. The y-axis shows deaths per
#|   million population on a scale from 0 to 50; the x-axis shows year. Two
#|   data points are shown: approximately 33 deaths per million in 2024 rising
#|   to around 35 in 2025. The small increase is consistent with the
#|   continuing rise in ambient temperatures from a warming climate.
RI_5E1_heat_stress_deaths_plot

```

### Findings
A small increase in deaths per million for the region is likely to reflect the ongoing increase in ambient temperature arising from a warming climate. WECA has produced a [Climate Adaptation Report](https://www.westofengland-ca.gov.uk/what-we-do/environment/climate-impact/) to help the region prepare for the impacts of a warming climate.

---

## Flood Warnings Intensity

```{r}
#| label: RI_5E2_flood_warning_index_gt
#| eval: true
#| code-summary: "summary"

indicator_fact_tbl |>
format_indicator_summary(
  "RI_5E2_flood_warning_index",
  title = "Flood Warnings Intensity Index",
  subtitle = "Relative to 2020 baseline",
  units = ""
)

```

### Overview

This indicator is designed to represent the risk of flooding relative to a 2020 baseline. It is a duration-weighted composite indicator tracking flood warning activity across the West of England (Bristol, Bath & North East Somerset, South Gloucestershire, North Somerset and derived from the Environment Agency's flood warnings dataset. It provides annual monitoring to support climate resilience reporting. The methodology for the indicator is described [here](https://github.com/stevecrawshaw/fwii).

```{r}
#| label: RI_5E2_flood_warning_index_plot
#| eval: true
#| code-summary: "RI_5E2_flood_warning_index plot"
#| fig-alt: |
#|   Line and point chart of the Flood Warning Intensity Index (FWII) for the
#|   West of England from 2020 to 2025. The y-axis shows the composite index
#|   value on a scale from 0 to 200; the x-axis shows year. A dashed green
#|   horizontal line marks the 2020 baseline at 100. The index fell sharply to
#|   around 40 in 2021 and 30 in 2022, returned to the baseline in 2023,
#|   peaked at approximately 165 in 2024, then dropped below the baseline to
#|   around 70 in 2025. The 2024 peak represents the highest flood warning
#|   intensity in the series.
RI_5E2_flood_warning_index_plot

```

### Findings

2024 saw the highest level of flooding relative to the 2020 baseline, but the levels of warnings subsided below the baseline in the most recent reported year. Warnings do not necessarily translate into actual floods.

---

## Tree Canopy

```{r}
#| label: RI_5F1_tree_canopy_gt
#| eval: true
#| code-summary: "summary"

indicator_fact_tbl |>
format_indicator_summary(
  "RI_5F1_tree_canopy",
  title = "Tree Canopy Cover",
  subtitle = "National Forest Inventory Woodland",
  units = "Ha")

```

### Overview

This indicator tracks the extent of tree canopy cover in the region, as measured by the National Forest Inventory (NFI). Tree canopy cover is an important aspect of urban greening, biodiversity and climate resilience. The NFI dataset is filtered by the "Woodland" category and clipped to the boundary of the West of England to provide a regional measure of the area covered by woodland.

```{r}
#| label: RI_5F1_tree_canopy_plot
#| eval: true
#| code-summary: "RI_5F1_tree_canopy plot"
#| fig-alt: |
#|   Line chart showing the percentage change in National Forest Inventory
#|   woodland extent in the West of England from the 2020 baseline, covering
#|   2020 to 2024. The y-axis shows percentage change on a scale from -1% to
#|   +1%; the x-axis shows year. The line remains very close to zero
#|   throughout, ending at approximately +0.3% by 2024, indicating a small
#|   but positive increase in woodland cover since 2020.

RI_5F1_plot

```

### Findings

The extent of woodland varies very little from year to year, but the overall trend is positive with a small increase in canopy cover since 2020. Several initiatives are underway to increase tree canopy cover in the region, including the [Forest of Avon](https://forestofavon.org/) project which is planting trees across the region to support biodiversity and climate resilience. These are likely to show in the indicator as the newly planted trees mature and are captured in the NFI dataset.


## Water Catchment Health

```{r}
#| label: RI_5F4_water_catchment_health_gt
#| eval: true
#| code-summary: "RI_5F4_water_catchment_health summary"

indicator_fact_tbl |>
format_indicator_summary(
  "RI_5F4_water_catchment_health",
  title = "Water Catchment Health",
  subtitle = "Proportion of surface waters in 'Good' ecological health",
  units = "%"
)
```

### Overview

This indicator tracks the ecological health of surface waters in the catchment which most closely represents the region - [Avon Bristol and Somerset North Streams](https://environment.data.gov.uk/catchment-planning/ManagementCatchment/3005/classifications). It is expressed as the proportion of surface waters in 'Good' ecological health. The data are derived from the Environment Agency's regular water quality monitoring programme. Surface water classification and sources have changed over the years, so data prior to 2019 are not comparable with recent datasets.

```{r}
#| label: RI_5F4_water_catchment_health_plot
#| eval: true
#| code-summary: "RI_5F4_water_catchment_health plot"
#| fig-alt: |
#|   Line and point chart of the proportion of surface waters in 'Good'
#|   ecological health in the Avon Bristol and Somerset North Streams
#|   catchment, for 2019 and 2022. The y-axis shows percentage from 0% to
#|   100%; the x-axis shows year. Both data points sit at approximately 14–15%,
#|   showing virtually no change and reflecting the national picture of
#|   persistently poor surface water quality.

RI_5F4_plot

```

### Findings

Data from recent years show little variation and reflect the national picture on the state of surface waters. The number of water bodies sampled has not changed significantly. Several sources of pollution impact water quality including agricultural run - off and untreated sewage discharge.


---

<!-- ## Indicator -->

<!-- ```{r} -->
<!-- #| label: _gt -->
<!-- #| eval: true -->
<!-- #| code-summary: "summary" -->

<!-- ``` -->

<!-- ### Overview -->

<!-- ```{r} -->
<!-- #| label: _plot -->
<!-- #| eval: true -->
<!-- #| code-summary: " plot" -->


<!-- ``` -->

<!-- ### Findings -->

<!-- --- -->

<!-- ## Indicator 4: Non-Domestic Energy Performance Certificates (EPC) A or A+ -->

<!-- ```{r} -->
<!-- #| label: _gt -->
<!-- #| eval: true -->
<!-- #| code-summary: "summary" -->

<!-- ``` -->

<!-- ### Overview -->

<!-- ```{r} -->
<!-- #| label: _plot -->
<!-- #| eval: true -->
<!-- #| code-summary: " plot" -->


<!-- ``` -->

<!-- ### Findings -->

<!-- --- -->



## Summary

Summary of key findings across all green economy indicators. What is the overall picture for green jobs and growth?

---
