---
title: "Green Jobs and Growth"
subtitle: "Making the West of England the home for green jobs and growth"
author: "SC"
date: last-modified
execute:
  echo: true
  warning: false
  message: false
---

## Context

This chapter tracks indicators related to green economy and environmental sustainability across the West of England. Up to 10 indicators can be included, covering metrics like green jobs, renewable energy, carbon emissions, electric vehicle uptake, and green business growth.

## Setup

```{r}
#| label: setup
#| code-summary: "Load required packages"
#| eval: true
#| message: false
#| warning: false
#| echo: false

# Load required packages
library(tidyverse)

# Source the WECA theme and helper functions
source(here::here("scripts", "R", "_common.R"))
source(here::here("scripts", "R", "load_pins.R"))
source(here::here("scripts", "R", "05-environment","RI_5_ghg_emissions.R"))
source(here::here("scripts", "R", "05-environment","RI_5A1_renewable.R"))
```

---

## Indicator 1: Greenhouse Gas Emissions

```{r}
#| label: RI_5_ghg_emissions_gt
#| eval: true
#| code-summary: "RI_5_ghg_emissions KPI summary"
collate_fact() |>
  build_reporting_view() |> 
format_indicator_summary(
  "RI_5_ghg_emissions",
  title = "Greenhouse Gas Emissions",
  subtitle = "Transport, Commercial, Industry, Public sector, Domestic",
  units = "Kt CO2e"
)
```

### Overview

Regional GHG emissions from transport, domestic, commercial, industrial and public sectors. This tracks the region's progress toward the net zero target by 2030 and identifies key sectors for emissions reduction.


```{r}
#| label: RI_5_ghg_emissions
#| eval: true
#| code-summary: "RI_5_ghg_emissions analysis"

# Your code here
RI_5_plot
# See chapters/01-economy/index.qmd for a worked example pattern:
# 1. Load data using load_csv()
# 2. Process/filter/aggregate data
# 3. Create visualization with theme_weca()
# 4. Calculate key statistics using format_number()
```

### Findings

Emissions have declined steadily over several years. Transport and domestic sectors dominate. The region is currently not on track to meet the 2030 net zero target, indicating a need for accelerated action in key sectors.
Demand reduction for personal car use and the introduction of low - carbon heating for homes remain key priorities for the region.

---

## Indicator 2: Renewable Energy

```{r}
#| label: RI_5A1_renewable_gt
#| eval: true
#| code-summary: "RI_5A1_renewable summary"

collate_fact() |>
  build_reporting_view() |> 
format_indicator_summary(
  "RI_5A1_renewable_capacity_km2",
  title = "Renewable Electricity Installed Capacity",
  subtitle = "Installed capacity per square Km",
  units = "MW/km2"
)

```
### Overview

Potential for renewable energy capacity is strongly influenced by land availability and price, hence this indicator is expressed in terms of Megawatts per square kilometre to enable future comparison with other regions.

```{r}
RI_5A1_renewable_plot
```

### Findings

Installed capacity has climbed steadily over the last 10 years, reflecting central government policy and the region's ambitions for Net Zero. The National Energy Systems Operator (NESO) is currently developing [regional energy strategic plans](https://www.neso.energy/what-we-do/strategic-planning/regional-energy-strategic-planning-resp) which may drive further growth in installed capacity.

---

## Summary

[Summary of key findings across all green economy indicators. What is the overall picture for green jobs and growth?]
