---
title: "Green Jobs and Growth"
subtitle: "Making the West of England the home for green jobs and growth"
author: "SC"
date: last-modified
execute:
  echo: true
  warning: false
  message: false
---

## Context

This chapter tracks indicators related to green economy and environmental sustainability across the West of England. Topics include carbon emissions, renewable energy, water pollution, climate resilience and public health.

```{r}
#| label: setup
#| code-summary: "Load required packages and source files"
#| eval: true
#| message: false
#| warning: false
#| echo: false
#| include: false

# Load required packages
library(tidyverse)

# Source the WECA theme and helper functions
source(here::here("scripts", "R", "_common.R"))
source(here::here("scripts", "R", "load_pins.R"))
source(here::here("scripts", "R", "05-environment","RI_5_ghg_emissions.R"))
source(here::here("scripts", "R", "05-environment","RI_5A1_renewable.R"))
source(here::here("scripts", "R", "05-environment","RI_5B1_nondom_epc_a.R"))
source(here::here("scripts", "R", "05-environment","RI_5E1_heat_stress_deaths.R"))

```

---

## Greenhouse Gas Emissions

```{r}
#| label: RI_5_ghg_emissions_gt
#| eval: true
#| code-summary: "RI_5_ghg_emissions KPI summary"
collate_fact() |>
  build_reporting_view() |> 
format_indicator_summary(
  "RI_5_ghg_emissions",
  title = "Greenhouse Gas Emissions",
  subtitle = "Transport, Commercial, Industry, Public sector, Domestic",
  units = "Kt CO2e"
)
```

### Overview

Regional greenhouse gas emissions from transport, domestic, commercial, industrial and public sectors. This tracks the region's progress toward the net zero target by 2030 and identifies key sectors for emissions reduction.

```{r}
#| label: RI_5_ghg_emissions
#| eval: true
#| code-summary: "RI_5_ghg_emissions analysis"
RI_5_plot
```

### Findings

Emissions have declined steadily over several years. Transport and domestic sectors dominate. The region is currently not on track to meet the 2030 net zero target, indicating a need for accelerated action in key sectors.
Demand reduction for personal car use and the introduction of low - carbon heating for homes remain key priorities for the region.

---

## Renewable Energy

```{r}
#| label: RI_5A1_renewable_gt
#| eval: true
#| code-summary: "RI_5A1_renewable summary"

collate_fact() |>
  build_reporting_view() |> 
format_indicator_summary(
  "RI_5A1_renewable_capacity_km2",
  title = "Renewable Electricity Installed Capacity",
  subtitle = "Installed capacity per square Km",
  units = "MW/km2"
)

```
### Overview

Potential for renewable energy capacity is strongly influenced by land availability and price, hence this indicator is expressed in terms of Megawatts per square Kilometre to enable future comparison with other regions.

```{r}
#| label: RI_5A1_renewable_plot
#| eval: true
#| code-summary: "RI_5A1_renewable plot bar chart"

RI_5A1_renewable_plot
```

### Findings

Installed capacity has climbed steadily over the last 10 years, reflecting central government policy and the region's ambitions for Net Zero. The National Energy Systems Operator (NESO) is currently developing [regional energy strategic plans](https://www.neso.energy/what-we-do/strategic-planning/regional-energy-strategic-planning-resp) which may drive further growth in installed capacity.

---

## Domestic Renewable Energy

```{r}
#| label: RI_5A2_domestic_renewable_gt
#| eval: true
#| code-summary: "RI_5A2_domestic_renewable summary"

collate_fact() |>
  build_reporting_view() |> 
format_indicator_summary(
  "RI_5A2_domestic_renewable",
  title = "Domestic Renewable Energy",
  subtitle = "Photovoltaic sites",
  units = "Sites per household"
)

```
### Overview

Solar photovoltaic (PV) installations are a key aspect of energy security and net zero. This indicator tracks installations per household in the region.

```{r}
#| label: RI_5A2_domestic_renewable_plot
#| eval: true
#| code-summary: "RI_5A2_domestic_renewable plot bar chart"
RI_5A2_domestic_renewable_plot

```

### Findings

Installations of PV panels have increased steadily over the last 10 years.

---

## Non-Domestic Energy Performance

```{r}
#| label: RI_5B1_nondom_epc_a_gt
#| eval: true
#| code-summary: "summary"
collate_fact() |>
  build_reporting_view() |> 
format_indicator_summary(
  "RI_5B1_nondom_epc_a",
  title = "Non - Domestic Energy Ratings",
  subtitle = "Proportion of properties rated A or A+",
  units = "%"
)

```

### Overview

This indicator measures the energy efficiency of non - domestic property by expressing the proportion of properties which have an energy rating of A or A+, in other words the best performing properties.

```{r}
#| label: RI_5B1_nondom_epc_a_plot
#| eval: true
#| code-summary: "RI_5B1_nondom_epc_a monthly cumulative plot"
#| 
RI_5B1_nondom_epc_a_plot

```

### Findings

The improvement in the proportion of properties meeting an A or A+ standard is slow but steady. WECA's Low Carbon Business Support team help businesses improve their energy efficiency with assessments, advice and grants.

---


## Heat Associated Mortality

```{r}
#| label: RI_5E1_heat_stress_deaths_gt
#| eval: true
#| code-summary: "summary"

collate_fact() |>
  build_reporting_view() |> 
format_indicator_summary(
  "RI_5E1_heat_stress_deaths",
  title = "Heat Associated Mortality",
  subtitle = "Deaths per million population",
  units = "deaths per million"
)

```

### Overview
This indicator tracks the number of heat associated deaths per million population in the Avon Local Resilience Forum area, which largely correlates with the West of England. It provides insight into the region's vulnerability to heat stress through the lens of public health. Data for the region are only available since 2024.

```{r}
#| label: _plot
#| eval: true
#| code-summary: "RI_5E1_heat_stress_deaths plot"
#| 
RI_5E1_heat_stress_deaths_plot

```

### Findings
A small increase in deaths per million for the region is likely to reflect the ongoing increase in ambient temperature arising from a warming climate. WECA has produced a [Climate Adaptation Report] (https://www.westofengland-ca.gov.uk/what-we-do/environment/climate-impact/) to help the region prepare for the impacts of a warming climate.



<!-- --- -->

<!-- ## Indicator -->

<!-- ```{r} -->
<!-- #| label: _gt -->
<!-- #| eval: true -->
<!-- #| code-summary: "summary" -->

<!-- ``` -->

<!-- ### Overview -->

<!-- ```{r} -->
<!-- #| label: _plot -->
<!-- #| eval: true -->
<!-- #| code-summary: " plot" -->


<!-- ``` -->

<!-- ### Findings -->

<!-- --- -->

<!-- ## Indicator -->

<!-- ```{r} -->
<!-- #| label: _gt -->
<!-- #| eval: true -->
<!-- #| code-summary: "summary" -->

<!-- ``` -->

<!-- ### Overview -->

<!-- ```{r} -->
<!-- #| label: _plot -->
<!-- #| eval: true -->
<!-- #| code-summary: " plot" -->


<!-- ``` -->

<!-- ### Findings -->

<!-- --- -->

<!-- ## Indicator -->

<!-- ```{r} -->
<!-- #| label: _gt -->
<!-- #| eval: true -->
<!-- #| code-summary: "summary" -->

<!-- ``` -->

<!-- ### Overview -->

<!-- ```{r} -->
<!-- #| label: _plot -->
<!-- #| eval: true -->
<!-- #| code-summary: " plot" -->


<!-- ``` -->

<!-- ### Findings -->

<!-- --- -->

<!-- ## Indicator -->

<!-- ```{r} -->
<!-- #| label: _gt -->
<!-- #| eval: true -->
<!-- #| code-summary: "summary" -->

<!-- ``` -->

<!-- ### Overview -->

<!-- ```{r} -->
<!-- #| label: _plot -->
<!-- #| eval: true -->
<!-- #| code-summary: " plot" -->


<!-- ``` -->

<!-- ### Findings -->

<!-- --- -->

<!-- ## Indicator 4: Non-Domestic Energy Performance Certificates (EPC) A or A+ -->

<!-- ```{r} -->
<!-- #| label: _gt -->
<!-- #| eval: true -->
<!-- #| code-summary: "summary" -->

<!-- ``` -->

<!-- ### Overview -->

<!-- ```{r} -->
<!-- #| label: _plot -->
<!-- #| eval: true -->
<!-- #| code-summary: " plot" -->


<!-- ``` -->

<!-- ### Findings -->

<!-- --- -->



## Summary

Summary of key findings across all green economy indicators. What is the overall picture for green jobs and growth?

---
