---
title: "Green Jobs and Growth"
subtitle: "Making the West of England the home for green jobs and growth"
author: "SC"
date: last-modified
execute:
  echo: true
  warning: false
  message: false
---

## Context

This chapter tracks indicators related to green economy and environmental sustainability across the West of England. Up to 10 indicators can be included, covering metrics like green jobs, renewable energy, carbon emissions, electric vehicle uptake, and green business growth.

## Setup

```{r}
#| label: setup
#| code-summary: "Load required packages"

# Load required packages
library(tidyverse)

# Source the WECA theme and helper functions
source(here::here("scripts", "R", "theme_weca.R"))
source(here::here("scripts", "R", "helpers.R"))
```

---

## Indicator 1: [Your Green Economy Indicator]

**Data source:** [Specify source]
**Last updated:** [Date]
**Refresh schedule:** [Annual/Quarterly/Monthly]

### Overview

[Describe what this indicator measures and why it matters for green jobs and growth]

```{r}
#| label: indicator-1
#| eval: false
#| code-summary: "Indicator 1 analysis"

# Your code here
# See chapters/01-economy/index.qmd for a worked example pattern:
# 1. Load data using load_csv()
# 2. Process/filter/aggregate data
# 3. Create visualization with theme_weca()
# 4. Calculate key statistics using format_number()
```

### Findings

[Your narrative findings here]

---

## Indicator 2: [Your Green Economy Indicator]

**Data source:**
**Last updated:**
**Refresh schedule:**

[Repeat structure - add up to 10 indicators total]

---

## Summary

[Summary of key findings across all green economy indicators. What is the overall picture for green jobs and growth?]
