---
title: "Economic Growth"
subtitle: "Contributing to national economic growth"
author: "SN"
date: last-modified
execute:
  echo: true
  warning: false
  message: false
---

## Context

This chapter tracks regional indicators related to the West of England's contribution to national economic growth. It includes indicators related to business growth, productivity, and innovation. The chapter draws on a range of national and local data sources to provide a high-level overview of regional trends and performance in relation to economic growth. Indicators were defined as part of the development of our [Growth Strategy](https://www.westofengland-ca.gov.uk/wp-content/uploads/2025/09/WE4915-Growth-Strategy-exec-summary_aw_web_v1.pdf) and are intended to provide a high-level overview of regional trends and performance in relation to economic growth.

```{r}
#| label: 01_setup
#| code-summary: "Load required packages and source files"
#| include: false

# Load required packages
library(tidyverse)

# Source shared helpers (theme, helpers, fact_helpers, collate_fact)
source(here::here("scripts", "R", "_common.R"))
# source(here::here("scripts", "R", "load_pins.R"))
source(here::here("scripts", "R", "01-economy", "RI_1D1_broadband_coverage.R"))

indicator_fact_tbl <- collate_fact() |>
  build_reporting_view()
```

---

## Broadband coverage

```{r}
#| label: RI_1D1_broadband_coverage
#| eval: true
#| code-summary: "RI_1D1_broadband_coverage KPI summary"
indicator_fact_tbl |>
format_indicator_summary(
  "RI_1D1_broadband_coverage",
  title = "Superfast coverage",
  subtitle = "Residential and commercial premises",
  units = "percent"
)
```

### Overview

Regional broadband coverage for residential and commercial premises. This tracks the region's progress in relation to superfast broadband coverage (30mbps+) and gigabit broadband coverage (1000mbps+).

```{r}
#| label: RI_1D1_broadband_coverage_plot
#| eval: true
#| code-summary: "RI_1D1_broadband_coverage analysis"
RI_1D1_plot
```

---
