---
title: "Economic Growth"
subtitle: "Contributing to national economic growth"
author: "SN"
date: last-modified
execute:
  echo: true
  warning: false
  message: false
---

## Context

This chapter tracks indicators related to the West of England's contribution to national economic growth. Up to 10 indicators can be included, covering metrics like GVA, productivity, business growth, innovation, and employment.

```{r}
#| label: 01_setup
#| code-summary: "Load required packages and source files"
#| include: false

# Load required packages
library(tidyverse)

# Source shared helpers (theme, helpers, fact_helpers, collate_fact)
source(here::here("scripts", "R", "_common.R"))
# source(here::here("scripts", "R", "load_pins.R"))
source(here::here("scripts", "R", "01-economy", "RI_1D1_broadband_coverage.R"))

indicator_fact_tbl <- collate_fact() |>
  build_reporting_view()
```

---

## Broadband coverage

```{r}
#| label: RI_1D1_broadband_coverage
#| eval: true
#| code-summary: "RI_1D1_broadband_coverage KPI summary"
indicator_fact_tbl |>
format_indicator_summary(
  "RI_1D1_broadband_coverage",
  title = "Superfast coverage",
  subtitle = "Residential and commercial premises",
  units = "percent"
)
```

### Overview

Regional broadband coverage for residential and commercial premises. This tracks the region's progress in relation to superfast broadband coverage (30mbps+) and gigabit broadband coverage (1000mbps+).

```{r}
#| label: RI_1D1_broadband_coverage_plot
#| eval: true
#| code-summary: "RI_1D1_broadband_coverage analysis"
RI_1D1_plot
```

---
