---
title: "Future-Ready Skills"
subtitle: "Empowering residents with future-ready skills"
author: "MJ"
date: last-modified
execute:
  echo: true
  warning: false
  message: false
---

## Context

This chapter tracks indicators related to skills development and training across the West of England. Up to 10 indicators can be included, covering metrics like qualification levels, apprenticeships, adult learning participation, skills gaps, and employment outcomes.

## Setup

```{r}
#| label: setup
#| code-summary: "Load required packages"

# Load required packages
library(tidyverse)

# Source the WECA theme and helper functions
source(here::here("scripts", "R", "theme_weca.R"))
source(here::here("scripts", "R", "helpers.R"))
```

---

## Indicator 1: [Your Skills Indicator]

**Data source:** [Specify source]
**Last updated:** [Date]
**Refresh schedule:** [Annual/Quarterly/Monthly]

### Overview

[Describe what this indicator measures and why it matters for future-ready skills]

```{r}
#| label: indicator-1
#| eval: false
#| code-summary: "Indicator 1 analysis"

# Your code here
# See chapters/01-economy/index.qmd for a worked example pattern:
# 1. Load data using load_csv()
# 2. Process/filter/aggregate data
# 3. Create visualization with theme_weca()
# 4. Calculate key statistics using format_number()
```

### Findings

[Your narrative findings here]

---

## Indicator 2: [Your Skills Indicator]

**Data source:**
**Last updated:**
**Refresh schedule:**

[Repeat structure - add up to 10 indicators total]

---

## Summary

[Summary of key findings across all skills indicators. What is the overall picture for future-ready skills development?]
