---
title: "Affordable and Sustainable Homes"
subtitle: "Creating and building affordable/sustainable homes"
author: "CJ"
date: last-modified
execute:
  echo: true
  warning: false
  message: false
---

## Context

This chapter tracks indicators related to housing affordability and sustainability across the West of England. Up to 10 indicators can be included, covering metrics like housing completions, affordability ratios, energy efficiency, social housing supply, and planning permissions.

## Setup

```{r}
#| label: setup
#| code-summary: "Load required packages and source files"
#| include: false

# Load required packages
library(tidyverse)

# Source shared helpers (theme, helpers, fact_helpers, collate_fact)
source(here::here("scripts", "R", "_common.R"))
source(here::here("scripts", "R", "03-place", "RI_3A2_homes_epc_c_plus.R"))

indicator_fact_tbl <- collate_fact() |>
  build_reporting_view()
```
---

## Energy Performance of Homes

```{r}
#| label: RI_3A2_homes_epc_c_plus_gt
#| eval: true
#| code-summary: "RI_3A2_homes_epc_c_plus summary"

indicator_fact_tbl |>
format_indicator_summary(
  "RI_3A2_homes_epc_c_plus",
  title = "Energy Performance of Homes",
  subtitle = "Proportion of homes with EPC rating of C or above",
  units = "%"
)

```

### Overview

This indicator tracks the proportion of homes in the West of England with an Energy Performance Certificate (EPC) rating of C or above. A higher proportion indicates better energy efficiency and sustainability in the housing stock. Only about 70% of homes have an EPC, so this indicator is based on the subset of homes with an EPC, which may not be fully representative of all homes in the region. This dataset is from [MHCLG](https://get-energy-performance-data.communities.gov.uk/) and is based on the recently revised scheme for EPC.

```{r}
#| label: RI_3A2_homes_epc_c_plus_plot
#| eval: true
#| code-summary: "RI_3A2_homes_epc_c_plus plot"

RI_3A2_plot

```
### Findings

The proportion of homes which have an EPC with an energy rating of C or better has risen steadily over the last 10 years. EPC ratings measure energy efficiency and are not directly related to carbon emissions. WECA runs programmes to help home owners and landlords understand [retrofit](https://www.retrofitwest.co.uk/) options and [businesses to reduce their carbon emissions](https://www.westofengland-ca.gov.uk/what-we-do/environment/low-carbon-business-support/).

---
<!-- ## Indicator -->

<!-- ```{r} -->
<!-- #| label: _gt -->
<!-- #| eval: true -->
<!-- #| code-summary: "summary" -->

<!-- ``` -->

<!-- ### Overview -->

<!-- ```{r} -->
<!-- #| label: _plot -->
<!-- #| eval: true -->
<!-- #| code-summary: " plot" -->


<!-- ``` -->

<!-- ### Findings -->

<!-- --- -->
<!-- ## Indicator -->

<!-- ```{r} -->
<!-- #| label: _gt -->
<!-- #| eval: true -->
<!-- #| code-summary: "summary" -->

<!-- ``` -->

<!-- ### Overview -->

<!-- ```{r} -->
<!-- #| label: _plot -->
<!-- #| eval: true -->
<!-- #| code-summary: " plot" -->


<!-- ``` -->

<!-- ### Findings -->

<!-- --- -->
<!-- ## Indicator -->

<!-- ```{r} -->
<!-- #| label: _gt -->
<!-- #| eval: true -->
<!-- #| code-summary: "summary" -->

<!-- ``` -->

<!-- ### Overview -->

<!-- ```{r} -->
<!-- #| label: _plot -->
<!-- #| eval: true -->
<!-- #| code-summary: " plot" -->


<!-- ``` -->

<!-- ### Findings -->

<!-- --- -->
<!-- ## Indicator -->

<!-- ```{r} -->
<!-- #| label: _gt -->
<!-- #| eval: true -->
<!-- #| code-summary: "summary" -->

<!-- ``` -->

<!-- ### Overview -->

<!-- ```{r} -->
<!-- #| label: _plot -->
<!-- #| eval: true -->
<!-- #| code-summary: " plot" -->


<!-- ``` -->

<!-- ### Findings -->

<!-- --- -->
<!-- ## Indicator -->

<!-- ```{r} -->
<!-- #| label: _gt -->
<!-- #| eval: true -->
<!-- #| code-summary: "summary" -->

<!-- ``` -->

<!-- ### Overview -->

<!-- ```{r} -->
<!-- #| label: _plot -->
<!-- #| eval: true -->
<!-- #| code-summary: " plot" -->


<!-- ``` -->

<!-- ### Findings -->

<!-- --- -->
<!-- ## Indicator -->

<!-- ```{r} -->
<!-- #| label: _gt -->
<!-- #| eval: true -->
<!-- #| code-summary: "summary" -->

<!-- ``` -->

<!-- ### Overview -->

<!-- ```{r} -->
<!-- #| label: _plot -->
<!-- #| eval: true -->
<!-- #| code-summary: " plot" -->


<!-- ``` -->

<!-- ### Findings -->

<!-- --- -->
<!-- ## Indicator -->

<!-- ```{r} -->
<!-- #| label: _gt -->
<!-- #| eval: true -->
<!-- #| code-summary: "summary" -->

<!-- ``` -->

<!-- ### Overview -->

<!-- ```{r} -->
<!-- #| label: _plot -->
<!-- #| eval: true -->
<!-- #| code-summary: " plot" -->


<!-- ``` -->

<!-- ### Findings -->

<!-- --- -->
<!-- ## Indicator -->

<!-- ```{r} -->
<!-- #| label: _gt -->
<!-- #| eval: true -->
<!-- #| code-summary: "summary" -->

<!-- ``` -->

<!-- ### Overview -->

<!-- ```{r} -->
<!-- #| label: _plot -->
<!-- #| eval: true -->
<!-- #| code-summary: " plot" -->


<!-- ``` -->

<!-- ### Findings -->

<!-- --- -->
<!-- ## Indicator -->

<!-- ```{r} -->
<!-- #| label: _gt -->
<!-- #| eval: true -->
<!-- #| code-summary: "summary" -->

<!-- ``` -->

<!-- ### Overview -->

<!-- ```{r} -->
<!-- #| label: _plot -->
<!-- #| eval: true -->
<!-- #| code-summary: " plot" -->


<!-- ``` -->

<!-- ### Findings -->

<!-- --- -->
<!-- ## Indicator -->

<!-- ```{r} -->
<!-- #| label: _gt -->
<!-- #| eval: true -->
<!-- #| code-summary: "summary" -->

<!-- ``` -->

<!-- ### Overview -->

<!-- ```{r} -->
<!-- #| label: _plot -->
<!-- #| eval: true -->
<!-- #| code-summary: " plot" -->


<!-- ``` -->

<!-- ### Findings -->

<!-- --- -->


## Summary

[Summary of key findings across all housing indicators. What is the overall picture for affordable and sustainable homes?]
