---
title: "Affordable and Sustainable Homes"
subtitle: "Creating and building affordable/sustainable homes"
author: "CJ"
date: last-modified
execute:
  echo: true
  warning: false
  message: false
---

## Context

This chapter tracks indicators related to housing affordability and sustainability across the West of England. Up to 10 indicators can be included, covering metrics like housing completions, affordability ratios, energy efficiency, social housing supply, and planning permissions.

## Setup

```{r}
#| label: setup
#| code-summary: "Load required packages"

# Load required packages
library(tidyverse)

# Source the WECA theme and helper functions
source(here::here("scripts", "R", "theme_weca.R"))
source(here::here("scripts", "R", "helpers.R"))
```

---

## Indicator 1: [Your Housing Indicator]

**Data source:** [Specify source]
**Last updated:** [Date]
**Refresh schedule:** [Annual/Quarterly/Monthly]

### Overview

[Describe what this indicator measures and why it matters for affordable and sustainable homes]

```{r}
#| label: indicator-1
#| eval: false
#| code-summary: "Indicator 1 analysis"

# Your code here
# See chapters/01-economy/index.qmd for a worked example pattern:
# 1. Load data using load_csv()
# 2. Process/filter/aggregate data
# 3. Create visualization with theme_weca()
# 4. Calculate key statistics using format_number()
```

### Findings

[Your narrative findings here]

---

## Indicator 2: [Your Housing Indicator]

**Data source:**
**Last updated:**
**Refresh schedule:**

[Repeat structure - add up to 10 indicators total]

---

## Summary

[Summary of key findings across all housing indicators. What is the overall picture for affordable and sustainable homes?]
