---
title: "Public Transport Connectivity"
subtitle: "Connecting the region through better public transport"
author: "HB"
date: last-modified
execute:
  echo: true
  warning: false
  message: false
---

## Context

This chapter tracks indicators related to public transport connectivity across the West of England. Up to 10 indicators can be included, covering metrics like bus ridership, punctuality, accessibility, network coverage, and passenger satisfaction.

## Setup

```{r}
#| label: setup
#| code-summary: "Load required packages"

# Load required packages
library(tidyverse)

# Source the WECA theme and helper functions
source(here::here("scripts", "R", "theme_weca.R"))
source(here::here("scripts", "R", "helpers.R"))
```

---

## Indicator 1: [Your Transport Indicator]

**Data source:** [Specify source]  
**Last updated:** [Date]  
**Refresh schedule:** [Annual/Quarterly/Monthly]  


### Overview

[Describe what this indicator measures and why it matters for public transport connectivity]

```{r}
#| label: indicator-1
#| eval: false
#| code-summary: "Indicator 1 analysis"

# Your code here
# See chapters/01-economy/index.qmd for a worked example pattern:
# 1. Load data using load_csv()
# 2. Process/filter/aggregate data
# 3. Create visualization with theme_weca()
# 4. Calculate key statistics using format_number()
```

### Findings

[Your narrative findings here]

---

## Indicator 2: [Your Transport Indicator]

**Data source:**
**Last updated:**
**Refresh schedule:**

[Repeat structure - add up to 10 indicators total]

---

## Summary

[Summary of key findings across all transport indicators. What is the overall picture for public transport connectivity?]
